MSHS COVID-19 Vaccinations

### 2021-09-29 Weekly_Arrivals_Future_Sched_Tracking.Rmd
Create file for tracking weekly arrivals and schedule data for vaccine pod huddle. Create new markdown file and render file for tracking dose 3 schedule data to support ambulatory operations team.

# Determine whether or not to update an existing repo
update_repo <- TRUE

@@

# Store today's date
today <- Sys.Date()

@@

# Create variable with doses
doses <- c("Dose1", "Dose2", "AllDoses")

@@

epic_sched_to_date <- epic_sched_to_date %>%
  mutate(
    # Determine whether appointment is for dose 1 or dose 2
    Dose = ifelse(str_detect(Type, "DOSE 1"), "Dose1",
                  ifelse(str_detect(Type, "DOSE 2"), "Dose2", NA)),
    # Determine appointment date, year, month, etc.
    ApptDate = date(Date),
    ApptYear = year(Date),
    ApptMonth = month(Date),
    ApptDay = day(Date),
    ApptWeek = week(Date),
    # Clean up department if it is duplicated in that column
    Department = ifelse(str_detect(Department, ","),
                        substr(Department, 1,
                               str_locate(Department, ",") - 1),
                        Department),
    # Group arrived, completed, and checked out appts as arrived
    Status = ifelse(`Appt Status` %in% c("Arrived", "Comp", "Checked Out"),
                    "Arr", `Appt Status`),
    # Update appointment status: classify any appts from prior days that are
    # still in scheduled as No Shows
    Status2 = ifelse(ApptDate < (today) & Status == "Sch", "No Show", Status),
    # Determine manufacturer based on immunization field
    Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived
      ifelse(Status2 != "Arr", NA,
             # Assume any visits without immunization record are Pfizer
             ifelse(is.na(Immunizations), "Pfizer",
                    # Any immunizations with Moderna in text classified as
                    # Moderna, otherwise Pfizer
                    ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
                           # Any immunizations with Johnson and Johnson are
                           # classified as J&J
                           ifelse(str_detect(Immunizations,
                                             "Johnson and Johnson"),
                                  "J&J", "Pfizer")))),
    # Determine week number of year
    WeekNum = format(ApptDate, "%U"),
    # Determine appointment day of week
    DOW = weekdays(ApptDate),
    # Determine if patient's zip code is in NYS
    NYZip = substr(`ZIP Code`, 1, 5) %in% ny_zips$zipcode,
    # Determine week number of vaccine efforts
    VaccWeek = as.numeric(floor((ApptDate - vacc_start_first_sun) / 7) + 1))

@@

# Roll up any Moderna administered at MSB for YWCA to MSH
epic_sched_to_date <- epic_sched_to_date %>%
  mutate(Site = ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH", Site))

@@

# Summarize schedule data for Epic sites by key stratification
epic_sched_summary <- epic_sched_to_date %>%
  filter(Status2 %in% c("Arr", "Sch") &
           ApptDate <= today + 7) %>%
  group_by(Site,
           Dose,
           VaccWeek,
           ApptDate,
           Status2) %>%
  summarize(Count = n(),
            .groups = "keep") %>%
  pivot_wider(names_from = Dose,
              values_from = Count) %>%
  mutate(AllDoses = sum(Dose1, Dose2, na.rm = TRUE)) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "AllDoses"),
               names_to = "Dose",
               values_to = "Count") %>%
  ungroup()

@@

```{r Format MSSN Tableau data}
# Melt MSSN data to format similar to Epic sites
mssn_admin_to_date <- mssn_admin %>%
  mutate(Site = "MSSN",
         Status2 = "Arr",
         ApptDate = as.Date(ApptDate, format = "%B %d, %Y"),
         VaccWeek = as.numeric(
           floor((ApptDate - vacc_start_first_sun) / 7 +1))) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "AllDoses"),
               names_to = "Dose",
               values_to = "Count")

@@

# Summarize today's arrived and scheduled doses -------------
todays_sched <- daily_sched_summary %>%
  filter(ApptDate == today) %>%
  group_by(Site, Dose, ApptDate, Status2) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  pivot_wider(names_from = Status2,
              values_from = AdminDoses) %>%
  mutate(Total = sum(Arr, Sch, na.rm = TRUE),
         VaccWeek = NULL) %>%
  pivot_longer(cols = c(Arr, Sch, Total),
               names_to = "ApptStatus",
               values_to = "Count") %>%
  pivot_wider(names_from = c(ApptDate, ApptStatus),
              names_prefix = "Today's Sched: ",
              values_from = c(Count))

@@

@@

##### All Doses
```{r Subset data and create kable for all doses administered}
all_doses <- system_wide_summary %>%
  filter(Dose == "AllDoses") %>%
  mutate(Dose = NULL)

vaccine_admin_summary(x = all_doses, dose = "All Doses")

@@

##### First Doses
<p></p>
```{r Subset data and create kable for first doses administered}
first_doses <- system_wide_summary %>%
  filter(Dose == "Dose1") %>%
  mutate(Dose = NULL)

vaccine_admin_summary(x = first_doses, dose = "Dose 1")

@@

<p></p>
##### Second Doses
<p></p>
```{r Subset data and create kable for second doses administered}
second_doses <- system_wide_summary %>%
  filter(Dose == "Dose2") %>%
  mutate(Dose = NULL)

vaccine_admin_summary(x = second_doses, dose = "Dose 2")

@@

>>>>

@@

# Store today's date
today <- Sys.Date()
yesterday <- today - 1

@@

vacc_week_dates_today <- all_dates %>%
  filter(Date <= today) %>%
  group_by(VaccWeek) %>%
  summarize(Dates =
              paste0(format(min(Date), "%m/%d/%y"),
                     "-",
                     format(max(Date), "%m/%d/%y")))

# Create variable with doses
doses <- c("Dose1", "Dose2", "Dose3", "AllDoses")

@@

epic_sched_to_date <- epic_sched_to_date %>%
  mutate(
    # Determine whether appointment is for dose 1 or dose 2
    Dose = ifelse(str_detect(Type, "DOSE 1"), 1,
                  ifelse(str_detect(Type, "DOSE 2"), 2,
                         ifelse(str_detect(Type, "DOSE 3"), 3, NA))),
    # Determine appointment date, year, month, etc.
    ApptDate = date(Date),
    ApptYear = year(Date),
    ApptMonth = month(Date),
    ApptDay = day(Date),
    ApptWeek = week(Date),
    # Clean up department if it is duplicated in that column
    Department = ifelse(str_detect(Department, ","),
                        substr(Department, 1,
                               str_locate(Department, ",") - 1),
                        Department),
    # Group arrived, completed, and checked out appts as arrived
    Status = ifelse(`Appt Status` %in% c("Arrived", "Comp", "Checked Out"),
                    "Arr", `Appt Status`),
    # Update appointment status: classify any appts from prior days that are
    # still in scheduled as No Shows
    Status2 = ifelse(ApptDate < (today) & Status == "Sch", "No Show", Status),
    # Determine manufacturer based on immunization field
    Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived
      ifelse(Status2 != "Arr", NA,
             # Assume any visits without immunization record are Pfizer
             ifelse(is.na(Immunizations), "Pfizer",
                    # Any immunizations with Moderna in text classified as
                    # Moderna, otherwise Pfizer
                    ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
                           # Any immunizations with Johnson and Johnson are
                           # classified as J&J
                           ifelse(str_detect(Department, "VISITING DOCS") |
                                    str_detect(Immunizations,
                                               "Johnson and Johnson"),
                                  "J&J", "Pfizer")))),
    # Determine week number of year
    WeekNum = format(ApptDate, "%U"),
    # Determine appointment day of week
    DOW = weekdays(ApptDate),
    # Determine if patient's zip code is in NYS
    NYZip = substr(`ZIP Code`, 1, 5) %in% ny_zips$zipcode,
    # Determine week number of vaccine efforts
    VaccWeek = as.numeric(floor((ApptDate - vacc_start_first_sun) / 7) + 1))

@@

# Manually update discrepancies in site/mfg/dose
epic_sched_to_date <- epic_sched_to_date %>%
  mutate(# Roll up any Moderna administered at MSB for YWCA to MSH
    Site = ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH", Site),
    # Manually correct any J&J doses erroneously documented as dose 2 and change to dose 1
    Dose = ifelse(Mfg %in% c("J&J") & Dose %in% c(2), 1, Dose))

@@

# Summarize schedule data for Epic sites by key stratification
epic_sched_summary <- epic_sched_to_date %>%
  filter(Status2 %in% c("Arr", "Sch") &
           ApptDate <= today + 7) %>%
  group_by(Site,
           Dose,
           VaccWeek,
           ApptDate,
           Status2) %>%
  summarize(Count = n(),
            .groups = "keep") %>%
  pivot_wider(names_from = Dose,
              names_prefix = "Dose",
              values_from = Count) %>%
  mutate(AllDoses = sum(Dose1, Dose2, Dose3, na.rm = TRUE)) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "Dose3", "AllDoses"),
               names_to = "Dose",
               values_to = "Count") %>%
  mutate(Count = replace_na(Count, 0)) %>%
  ungroup()

@@

```{r Format MSSN Tableau data}
# Melt MSSN data to format similar to Epic sites
mssn_admin_to_date <- mssn_admin %>%
  mutate(Site = "MSSN",
         Status2 = "Arr",
         ApptDate = as.Date(ApptDate, format = "%B %d, %Y"),
         VaccWeek = as.numeric(
           floor((ApptDate - vacc_start_first_sun) / 7 +1)),
         Dose3 = NA) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "Dose3", "AllDoses"),
               names_to = "Dose",
               values_to = "Count") %>%
  mutate(Count = replace_na(Count, 0))

@@

# Summarize today's arrived and scheduled doses -------------
todays_sched <- daily_sched_summary %>%
  filter(ApptDate == today) %>%
  group_by(Site, Dose, ApptDate, Status2) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  pivot_wider(names_from = Status2,
              values_from = AdminDoses) %>%
  mutate(Sch = 0,
         Total = sum(Arr, Sch, na.rm = TRUE),
         VaccWeek = NULL) %>%
  pivot_longer(cols = c(Arr, Sch, Total),
               names_to = "ApptStatus",
               values_to = "Count") %>%
  pivot_wider(names_from = c(ApptDate, ApptStatus),
              names_prefix = "Today's Sched: ",
              values_from = c(Count))

@@

```{r Alternate format}
arr_visits <- daily_sched_summary %>%
  filter(Status2 %in% c("Arr")) %>%
  group_by(Site, Dose, VaccWeek) %>%
  summarize(Count = sum(Count, na.rm = TRUE))

arr_visits <- left_join(arr_visits,
                        vacc_week_dates_today,
                        by = c("VaccWeek" = "VaccWeek"))
arr_visits <- arr_visits %>%
  arrange(Site, Dose, VaccWeek) %>%
  mutate(WkDate = paste0("Wk ", VaccWeek, ": ", Dates),
         VaccWeek = NULL,
         Dates = NULL)

arr_visits_totals <- arr_visits %>%
  pivot_wider(names_from = c(Dose, WkDate),
              names_sep = "__",
              values_from = Count) %>%
  adorn_totals(where = "row",
               na.rm = TRUE,
               name = "MSHS") %>%
  pivot_longer(cols = contains("__", ignore.case = TRUE),
               names_to = c("Dose", "Week"),
               names_sep = "__",
               values_to = "Count") %>%
  mutate(Count = replace_na(Count, 0)) %>%
  pivot_wider(names_from = c(Site, Dose),
              names_sep = "__",
              values_from = Count) %>%
  adorn_totals(where = "row",
               na.rm = TRUE,
               name = "TotalDosesAdmin") %>%
  pivot_longer(cols = contains("__", ignore.case = TRUE),
               names_to = c("Site", "Dose"),
               names_sep = "__",
               values_to = "Count") %>%
  relocate(Site) %>%
  relocate(Dose, .after = Site) %>%
  pivot_wider(names_from = Week,
              values_from = Count) %>%
  relocate(TotalDosesAdmin, .after = Dose) %>%
  mutate(Site = factor(Site, levels = c(all_sites, "MSHS"), ordered = TRUE),
         Dose = factor(Dose, levels = doses, ordered = TRUE)) %>%
  arrange(Site, Dose)

arr_visits_kable <- function(dose) {
  if (!(dose %in% c(1, 2, 3, "All"))) {
    msg <- "Invalid argument"
    stop(msg)
  } else {
    dose_filter <- ifelse(dose %in% c(1:3), paste0("Dose", dose),
                          paste0(dose, "Doses"))

    dose_title <- ifelse(dose %in% c(1:3), paste("Dose", dose),
                         paste (dose, "Doses"))
    arr_visits_kable_df <<- arr_visits_totals %>%
      filter(Dose == dose_filter) %>%
      mutate(Dose = NULL) %>%
      rename(`Admin Doses to Date` = TotalDosesAdmin)

    arr_visits_kable_headers <- 
      c(" " = 2,
        "Administered Doses by Week" = ncol(arr_visits_kable_df) - 2)

    kable(arr_visits_kable_df, format = "html", escape = FALSE,
        align = "c", digits = 0,
        caption = paste0(dose_title, ": Administered Doses To Date")) %>%
    kable_styling(bootstrap_options = "hover", position = "center",
                  font_size = 11, full_width = FALSE) %>%
    column_spec(column = c(1,
                           2,
                           ncol(arr_visits_kable_df)),
                border_right = "thin solid lightgray") %>%
    column_spec(column = c(3:ncol(arr_visits_kable_df)),
                background = sinai_colors[2]) %>%
    row_spec(row = nrow(arr_visits_kable_df),
             background = "lightgrey",
             bold = T,
             italic = T,
             color = "black") %>%
    add_header_above(arr_visits_kable_headers,
                     background = c("",
                                    sinai_colors[1]),
                     line = FALSE,
                     color = "white") %>%
    scroll_box(width = "800px")
  }
}

# arr_visits_kable(dose = 3)
# 
# 
# arr_visits_kable_df <- arr_visits_totals %>%
#   filter(Dose == "AllDoses") %>%
#   mutate(Dose = NULL) %>%
#   rename(`Admin Doses to Date` = TotalDosesAdmin)
# 
# arr_visits_kable_headers <- 
#   c(" " = 2,
#     "Admin Doses by Week" = ncol(arr_visits_kable_df) - 2)
# 
# 
# kable(arr_visits_kable_df, format = "html", escape = FALSE,
#         align = "c", digits = 0,
#         caption = paste0("All Doses", " Summary")) %>%
#     kable_styling(bootstrap_options = "hover", position = "center",
#                   font_size = 11, full_width = FALSE) %>%
#     column_spec(column = c(1,
#                            2,
#                            ncol(arr_visits_kable_df)),
#                 border_right = "thin solid lightgray") %>%
#     column_spec(column = c(3:ncol(arr_visits_kable_df)),
#                 background = sinai_colors[2]) %>%
#     row_spec(row = nrow(arr_visits_kable_df),
#              background = "lightgrey",
#              bold = T,
#              italic = T,
#              color = "black") %>%
#     add_header_above(arr_visits_kable_headers,
#                      background = c("",
#                                     sinai_colors[1]),
#                      line = FALSE,
#                      color = "white") %>%
#     scroll_box(width = "800px")

sch_visits <- daily_sched_summary %>%
  filter(Status2 %in% c("Sch")) %>%
  group_by(Site, Dose, ApptDate) %>%
  summarize(Count = sum(Count, na.rm = TRUE))

# Create template of today through the next 7 days for each site and dose to ensure holidays are included
today_to_7days <- seq(from = today, to = today + 7, by = 1)

today_to_7days_rep <- data.frame("ApptDate" = rep(today_to_7days,
                                          length(all_sites)))

site_today_to_7days_rep <- data.frame("Site" = sort(rep(all_sites,
                                                        length(today_to_7days))))

site_today_to_7days_templ <- cbind(site_today_to_7days_rep, today_to_7days_rep)

site_dose_today_to_7days_templ <- left_join(site_dose_rep,
                                            site_today_to_7days_templ,
                                            by = c("Site" = "Site"))

sch_visits <- left_join(site_dose_today_to_7days_templ,
                          sch_visits,
                          by = c("Site" = "Site",
                                 "Dose" = "Dose",
                                 "ApptDate" = "ApptDate"))

sch_visits_totals <- sch_visits %>%
  mutate(Count = replace_na(Count, 0)) %>%
  arrange(Site, Dose, ApptDate) %>%
  pivot_wider(names_from = c(Dose, ApptDate),
              names_sep = "__",
              values_from = Count,
              names_sort = FALSE) %>%
  adorn_totals(where = "row",
               na.rm = TRUE,
               name = "MSHS") %>%
  pivot_longer(cols = contains("__", ignore.case = TRUE),
               names_to = c("Dose", "Date"),
               names_sep = "__",
               values_to = "Count") %>%
  mutate(Date = format(as.Date(Date, "%Y-%m-%d"), "%m/%d")) %>%
  pivot_wider(names_from = c(Site, Dose),
              names_sep = "__",
              values_from = Count) %>%
  adorn_totals(where = "row",
               na.rm = TRUE,
               name = "Total") %>%
  pivot_longer(cols = contains("__", ignore.case = TRUE),
               names_to = c("Site", "Dose"),
               names_sep = "__",
               values_to = "Count") %>%
  relocate(Site) %>%
  relocate(Dose, .after = Site) %>%
  mutate(Site = factor(Site, levels = c(all_sites, "MSHS"), ordered = TRUE),
         Dose = factor(Dose, levels = doses, ordered = TRUE)) %>%
  arrange(Site, Dose) %>%
  pivot_wider(names_from = Date,
              values_from = Count)

# sch_visits_kable_df <-sch_visits_totals %>%
#   filter(Dose == "AllDoses") %>%
#   mutate(Dose = NULL)
# 
# sch_visits_kable_headers <- 
#   c(" " = 1,
#     "Scheduled Appointments" = ncol(sch_visits_kable_df) - 1)
# 
# 
# kable(sch_visits_kable_df, format = "html", escape = FALSE,
#         align = "c", digits = 0,
#         caption = paste0("All Doses", " Summary")) %>%
#     kable_styling(bootstrap_options = "hover", position = "center",
#                   font_size = 11, full_width = FALSE) %>%
#     column_spec(column = c(1,
#                            ncol(sch_visits_kable_df) - 1,
#                            ncol(sch_visits_kable_df)),
#                 border_right = "thin solid lightgray") %>%
#     row_spec(row = nrow(sch_visits_kable_df),
#              background = "lightgrey",
#              bold = T,
#              italic = T,
#              color = "black") %>%
#     add_header_above(sch_visits_kable_headers,
#                      background = c("",
#                                     sinai_colors[1]),
#                      line = FALSE,
#                      color = "white") %>%
#     scroll_box(width = "800px")

sch_visits_kable <- function(dose) {
  if (!(dose %in% c(1, 2, 3, "All"))) {
    msg <- "Invalid argument"
    stop(msg)
  } else {
    dose_filter <- ifelse(dose %in% c(1:3), paste0("Dose", dose),
                          paste0(dose, "Doses"))

    dose_title <- ifelse(dose %in% c(1:3), paste("Dose", dose),
                         paste (dose, "Doses"))
    sch_visits_kable_df <- sch_visits_totals %>%
      filter(Dose == dose_filter) %>%
      mutate(Dose = NULL)

    sch_visits_kable_headers <-
      c(" " = 1,
        "Scheduled Appointments" = ncol(sch_visits_kable_df) - 1)

    kable(sch_visits_kable_df, format = "html", escape = FALSE,
          align = "c", digits = 0,
          caption = paste0(dose_title, ": Scheduled Appointments")) %>%
      kable_styling(bootstrap_options = "hover", position = "center",
                    font_size = 11, full_width = FALSE) %>%
      column_spec(column = c(1,
                             ncol(sch_visits_kable_df) - 1,
                             ncol(sch_visits_kable_df)),
                  border_right = "thin solid lightgray") %>%
      row_spec(row = nrow(sch_visits_kable_df),
               background = "lightgrey",
               bold = T,
               italic = T,
               color = "black") %>%
      add_header_above(sch_visits_kable_headers,
                       background = c("",
                                      sinai_colors[1]),
                       line = FALSE,
                       color = "white")
  }
}

@@

##### All Doses
```{r Subset data and create kable for all doses administered}
# all_doses <- system_wide_summary %>%
#   filter(Dose == "AllDoses") %>%
#   mutate(Dose = NULL)
# 
# vaccine_admin_summary(x = all_doses, dose = "All Doses")

arr_visits_kable(dose = "All")

asis_output("<h3>  </h3>")

sch_visits_kable(dose = "All")

@@

##### First Doses
<p></p>
```{r Subset data and create kable for first doses administered}
# first_doses <- system_wide_summary %>%
#   filter(Dose == "Dose1") %>%
#   mutate(Dose = NULL)
# 
# vaccine_admin_summary(x = first_doses, dose = "Dose 1")

arr_visits_kable(dose = 1)

asis_output("<h3>  </h3>")

sch_visits_kable(dose = 1)

@@

<p></p>
##### Second Doses
<p></p>
```{r Subset data and create kable for second doses administered}
# second_doses <- system_wide_summary %>%
#   filter(Dose == "Dose2") %>%
#   mutate(Dose = NULL)
# 
# vaccine_admin_summary(x = second_doses, dose = "Dose 2")

arr_visits_kable(dose = 2)

asis_output("<h3>  </h3>")

sch_visits_kable(dose = 2)

@@

<p></p>
##### Third Doses
<p></p>
```{r Subset data and create kable for third doses administered}
# third_doses <- system_wide_summary %>%
#   filter(Dose == "Dose3") %>%
#   mutate(Dose = NULL)
# 
# vaccine_admin_summary(x = third_doses, dose = "Dose 3")

arr_visits_kable(dose = 3)

asis_output("<h3>  </h3>")

sch_visits_kable(dose = 3)
